---
title: "MARK4265 Assignment 2-AM"
author: "Allison Mariana"
date: "October 5, 2018"
output: word_document
---
Q1: Please do the following work:
a). Create a vector “myColumn” with 10 numerical elements, transfer it into an R dataframe
b). Save it as a csv file “myV.csv” You can choose any location for the file
c). Save it as a text file “myV.txt” You can choose any location for the file
d). Import the data from myV.txt into a dataframe “myData” and list the data from “myData”
e). Get the mean of “myColumn”

a).
```{r hide=T}
library(ggplot2)
```
```{r}
myColumn<-c(10,11,5,-1,0,77,100,88,97,-78)
myColumn<-as.data.frame(myColumn)
```
b).
```{r}
write.csv(myColumn, file = "myV.csv")
```

c).
```{r}
write.table(myColumn, file = "C:\\Users\\Gaya\\Desktop\\myV.txt", sep = "\t",
            row.names = TRUE, col.names = NA)
```

d).
```{r}
myData<-read.delim("C:\\Users\\Gaya\\Desktop\\myV.txt", header = TRUE, sep = "\t", dec = ".")
myData
```

e).
```{r}
mean(myData$myColumn)
```



Q2: Please do the following work:
a). Import the data from the file “myTable.txt” Inspect the data
b). Assign the three variable in “myTable.txt” as y1, y2, and y3. 
c). Create a stem-and-leaf plot for y1 
d). Create a histogram for y2
e). Create a scatterplot for y2 and y3
f). Create a 3D scatterplot for y1, y2, and y3

a).
```{r}
myData<-read.delim("C:\\Users\\Gaya\\Desktop\\myTable.txt", header = TRUE, sep = "\t", dec = ".")
myData
View(myData)
```

b).
```{r}
colnames(myData)<-c('y1','y2','y3')
myData
```

c).
```{r}
stem(myData$y1)
```

d).
```{r}
hist(myData$y2) # using base
ggplot(myData,aes(myData$y2))+geom_histogram() #using ggplot
```

e).
```{r}
plot(myData$y2,myData$y3) # using base
ggplot(myData,aes(myData$y2,myData$y3))+geom_point() #using ggplot
```

f).
```{r}
# install.packages('scatterplot3d')
library(scatterplot3d)
s3d<-scatterplot3d(myData[1:3],
                   pch=16,
                   highlight.3d = TRUE,
                   type = 'h',
                   main='3D Scatteplot of myData')
```

Q3: Please do the following work:
a). Load the built-in dataframe “mpg” after library(tidyverse)
b). Use ggplot() and other function to draw the scatterplot for x=cyl, and y=hwy. Please color and size for “manufacturer”

a).
```{r}
library(tidyverse)
data('mpg')
```

b).
```{r}
library(ggplot2)
ggplot(mpg,aes(mpg$cyl,mpg$hwy,color=mpg$manufacturer,size=mpg$manufacturer))+geom_point()
```